Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-21 output/paper/_si.qmd
Writing results.
Finished describing main results and modification by sex.

## Figures for main results

### Average dose-response functions for significant results

```{r}
targets::tar_load(
  dplyr::matches("marginal_gcomp_(\\d)$"),
  store = store
)
```

::: {#suppfig-adrfs-rq3}
```{r adrfs-rq3}
#| fig-width: 6
#| fig-height: 7

exposures_of_interest <- c(
  "cortisol production",
  "X11bHSD"
)
ret_adrfs <- lapply(
  exposures_of_interest, function(x) {
    plot_adrf(
      df_preds = marginal_gcomp_3 |>
        tidylog::filter(
          variable == x
        )
    )
  }
)
ret_adrfs[[1]]
#ret_adrfs[[2]]
```
Average dose-response functions for...
:::

@@

>>>>

@@

### Sensitivity to exposure assessment

### 2023-12-21 output/paper/_tables.qmd
Finished describing main results and modification by sex.

# Tables for main results

## Marginal comparisons

```{r}
#| eval: false
#| echo: false

targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
```

```{r marginal-1}
#| eval: false
#| echo: false
#| label: tbl-marginal-1
#| tbl-cap: Marginal comparison results for $hitrtse \sim edc$

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r marginal-2}
#| eval: false
#| echo: false
#| label: tbl-marginal-2
#| tbl-cap: Marginal comparison results for $metabolite \sim edc$

tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

```{r marginal-3}
#| eval: false
#| echo: false
#| label: tbl-marginal-3
#| tbl-cap: Marginal comparison results for $hitrtse \sim metabolite$

tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

@@

## Marginal hypothesis

>>>>

@@

## Marginal hypotheses for effect modification

### 2023-12-21 output/paper/manuscript.qmd
Finished describing main results and modification by sex.

@Fig-marginal-3 presents the forest plot for the marginal effects of the corticosteroids on \acr{hitrtse}.

Results are presented as effect estimate of the marginal contrast and the $95\%$ \acr{ci}.

suppfig-adrfs-rq...

@@

- Report other analyses done (e.g., analyses of subgroups and interactions, and sensitivity analyses).

@@

# Funding

>>>>

@Fig-marginal-3 presents the forest plot for the marginal effects of the corticosteroids on \acr{hitrtse}. All marginal contrasts included the null, with no clear indication of directionality of the effect.

@@

### Effect modification by sex

targets::tar_load(
  dplyr::matches("marginal_hypothesis_(\\d)SA$"),
  store = store
)
heffects1 <- tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$numerical_results
heffects2 <- tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$numerical_results
heffects3 <- tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$numerical_results
```

Basic summary statistics of the estimated balancing weights for effect modification are presented in Tables [-@supptbl-weights-1sa; -@supptbl-weights-2sa; -@supptbl-weights-3sa]. As expected, the median value of the weights for each exposure was close to $1.00$.

@Tbl-hypothesis-1 presents the results of a hypothesis test for the difference between estimates of the marginal contrasts for females and males, for each exposure. Significant differences were present for the phenol OXBE (`r format_res(heffects1, "oxbe", "hitrtse")`) and the phthalate metabolites MEP (`r format_res(heffects1, "mep", "hitrtse")`) and MbZP (`r format_res(heffects1, "mbzp", "hitrtse")`). The forest plot of the individual marginal contrasts is presented in @suppfig-marginal-1sa.

@Tbl-hypothesis-2 presents the results of a hypothesis test for the difference between estimates of the marginal contrasts for females and males, for each exposure and outcome. Significant differences were present across all three classes of \acr{edcs} and for all outcomes. The largest differences were attributable to the \acr{opps} DMTP (cortisol production, `r format_res(heffects2, "dmtp", "cortisol production")`) and DETP (corticosterone production, (`r format_res(heffects2, "detp", "corticosterone production")`); cortisone production, (`r format_res(heffects2, "detp", "cortisone production")`)). The forest plots of the individual marginal contrasts are presented in @suppfig-marginal-2sa.

@Tbl-hypothesis-3 presents the results of a hypothesis test for the difference between estimates of the marginal contrasts for females and males, for each exposure. Significant differences were present for cortisone production (`r format_res(heffects3, "cortisone prod.", "hitrtse")`) and corticosterone production (`r format_res(heffects3, "corticost. prod.", "hitrtse")`). Furthermore, for all exposures, the marginal contrasts had opposite sign (positive for males and negative for females). The forest plot of the individual marginal contrasts is presented in @suppfig-marginal-3sa.

### Sensitivity to exposure assessment

@@
